---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# rmdal0

An attempt, minimal proof of concept. 


## setup MDAL

```bash
git clone https://github.com/lutraconsulting/MDAL.git
cd MDAL
mkdir build;cd build
## DONE AS ROOT, BECAUSE otherwise fail for some reason
cmake -DCMAKE_BUILD_TYPE=Rel -DENABLE_TESTS=ON  ..
make
make all install
```

Run the init thing for the C++ in this package: 

```{r init, eval=FALSE, include = TRUE}
tools::package_native_routine_registration_skeleton("../rmdal0", "src/init.c",character_only = FALSE)
```

Run the package, currently only calls [MDAL_Status()](https://github.com/lutraconsulting/MDAL/blob/0.3.3/mdal/mdal.cpp) as a minimal test. 

All going well it should return the value `2` and print out "mdalinfo 0". 

```{r minimal, }
rmdal0:::rmdal0()
```

---
Please note that the 'rmdal0' project is released with a
  [Contributor Code of Conduct](https://github.com/mdsumner/rmdal0/blob/master/CODE_OF_CONDUCT.md).
  By contributing to this project, you agree to abide by its terms.
